\textcolor{r_s}{Displacement Detection from GNSS Kinematic Positioning Using Bayesian Inference for Deformation Monitoring}

### 2021-09-23 paper/r1/manuscript-mssp.tex
exp

	\subsection{Simulation Experiment}
	In the experiment, we only simulate the up coordinate component, in which Gaussian white noise with the mean of 0 mm and the standard deviation of 30 mm is added.
	At 1000 s, 2500 s, and 3200 s, the displacements of -50 mm, -50 mm, and 100 mm are added, respectively. 
	The simulation results are shown in Fig. \ref{fig_v_sim_simple_gauss_ts}.

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_sim_simple_gauss_ts}
		\caption{Simulation data with multiple displacement change points.}
		\label{fig_v_sim_simple_gauss_ts}
	\end{figure} 
	As shown in Fig. \ref{fig_v_sim_simple_gauss_ts}, the whole time series is divided into four segments by three displacement change points. 
	Using the model designed above, Bayesian inference is implemented by the MCMC sampling. 
	The posterior sample distribution of $\bf{\tau}$ is shown in Fig. \ref{fig_v_tau_sim_simple}.

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_tau_sim_simple}
		\caption{Posterior sample distribution of $\tau$ in the simulation experiment.}
		\label{fig_v_tau_sim_simple}
	\end{figure} 
	As can be seen from Fig. \ref{fig_v_tau_sim_simple}, all the designed displacement change points are identified. 
	$\tau_3$ is the easiest to be identified, mainly due to the largest displacement amplitude. 
	Since the displacement amplitude at $\tau_2$ is small and there are fewer sample points on the right side, the estimated accuracy is worse than the other two change points.
	The histogram of the posterior sample of $\bf{\mu}$ is shown in Fig. \ref{fig_v_mu_sim_simple}.

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_mu_sim_simple}
		\caption{Histogram of posterior estimation of $\mu$ in the simulation experiment.}
		\label{fig_v_mu_sim_simple}
	\end{figure} 
	The blue curve in Fig. \ref{fig_v_mu_sim_simple} is the fitting result of \textcolor{r_s}{the} Gaussian distribution of the histogram.
	Although we assume that the prior distribution of $\bf{\mu}$ in the model obeys a uniform distribution, the posterior sample approximately obeys normal distribution. 
	The vertical green dashed line in Fig. \ref{fig_v_mu_sim_simple} represents the mean value of posterior samples, and the mean values of the four segments are 1.17 mm, -49.58 mm, -98.9 mm, and -3.65 mm.
	Among these means, $\mu_2$ has the highest accuracy, and its corresponding posterior sample coverage is the narrowest. 
	The estimation accuracy of $\mu_4$ is the lowest, and the corresponding posterior sample coverage is the widest. 
	These are mainly due to the fact that the most observation samples are used for $\mu_2$ estimation, while the least observation samples are used for $\mu_4$ estimation. 
	As shown in Fig. \ref{fig_v_sigma_sim_simple}, $\sigma$ is also accurately estimated.

	% 仿真实验中不同基于索引检测方法的指标值如图6所示。
	% 从中可以看出不同探测方法所采用的指标的数值范围不一致，但在所设计的突变处很明显。
	%  然而，想基于这些指标值自动将这些突变点识别出来，还需要额外的工作。
	%  另外，这些方法设计之初为了探测突变点，并未涉及位移提取。
	%  有学者，基于设计了基于这些指标的突变探测和位移提取方法，但实时过程复杂。
	%  相比而言，本文提出的方法是一种简单直接易于实现的一站式方法。
	The index values of different index-based detection methods in the simulation experiment are shown in Fig. \ref{fig_v_sim_idx}.
	It can be seen that the numerical range of indicators used by different detection methods is not consistent, but all are obvious at the designed abrupt point.
	However, to automatically identify these abrupt points based on these index values, additional work is required, such as setting a certain threshold.
	In addition, these methods were originally designed to detect abrupt points without involving displacement extraction.
	There are abrupt detection and displacement extraction methods based on these indicators, but the implementation process is complex\cite{shen_shortterm2021}.
	In contrast, the method proposed in this work is a simple, straightforward, and easy-to-implement one-stop method.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_sigma_sim_simple}
		\caption{Histogram of posterior sample of $\sigma$ in the simulation experiment.}
		\label{fig_v_sigma_sim_simple}
	\end{figure} 
	\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.45]{v_sim_idx}
	\caption{Index values of different index-based detection methods in simulation experiments.}
	\label{fig_v_sim_idx}
	\end{figure} 
	\subsection{Field Experiments}
	The experiments were carried out on the roof of a building on the campus of Wuhan University, and the equipment deployment is shown in Fig. \ref{fig_v_field_exp_config}. 
	A hard plank was pressed with large stones to ensure that the plank remains as fixed as possible during moving the object hanging on the plank. 
	One receiver antenna was fixed on the plank as a rover, and the other receiver antenna was installed on a tripod beside it as the base station. 
	Both antennas were connected to BD992 OEM boards on the table, and the OEM boards were connected to the laptops for data collection. 
	As shown in subgraphs (c) and (d), the height of the antenna was measured with a tape before and after each movement of the object hanging on the plank. 
	\textcolor{r_s}{
		The minimum scale of the tape is 1 mm, that is, the accuracy of the tape is 1 mm, and the estimated reading is 0.1 mm.
		Take five readings for each measurement to ensure the accuracy and reliability of the data.
	}
	Besides, markers are made on the ground and on the antenna respectively to ensure that the same position was referenced for each measurement. 
	The sampling frequency of the GNSS receiver is set to 1 Hz. 
	We did two experiments, each lasting nearly 45 minutes. 
	During the experiment, the object hanging on the board was manually moved several times.
	The displacement amplitude of the second experiment is smaller than that of the first experiment.
	The GNSS observation data collected above are processed by the open-source software RTKLIB\cite{takasu2011rtklib}. 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.5]{v_field_exp_config}
		\caption{Filed experiment configuration. (a) Overview; (b) Working platform; (c) Displacement control platform; (d) Displacement measurement by tape. }
		\label{fig_v_field_exp_config}
	\end{figure}

	\subsubsection{Field Experiment 1}%rover_bd9_3
	GNSS observations were processed epoch by epoch by using RTK mode, and the corresponding coordinate output was the only input of the proposed displacement detection method.
	The results of RTK positioning are shown in Fig. \ref{fig_v_bd9_3_up_tau}.
	Only the vertical displacement was triggered in the experiment, so only the up coordinate component is displayed. 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_ts}
		\caption{The up component of coordinates obtained by RTK positioning in field experiment 1.}
		\label{fig_v_bd9_3_up_ts}
	\end{figure}

	For such a short baseline, most of the errors can be eliminated by the double-difference observation. 
	As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as the multipath error that have not been eliminated. 
	The RTK positioning results are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling. 
	The histogram of the posterior sample of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau}.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_tau}
		\caption{Posterior sample distribution of $\tau$ in field experiment 1.}
		\label{fig_v_bd9_3_up_tau}
	\end{figure} 
	From the posterior sample distribution of $\tau_2$ in Fig. \ref{fig_v_bd9_3_up_tau}, one of the change points can be identified as 1897 s. 
	According to the maximum value in the bar chart of the posterior sample of $\tau_1$, the change point is identified as 781 s.
	However, as can be seen from Fig. \ref{fig_v_bd9_3_up_tau}, there are two peaks in the posterior sample distribution of change point $\tau_1$.
	The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object. 
	In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}. 
	The index values of different index-based detection methods in \textcolor{r_s}{the} field experiment 1 are shown in Fig. \ref{fig_v_exp1_idx}. At the abrupt point, each index value is no longer as clear as in the simulation experiment, which puts forward higher requirements for additional analysis of these indexes.
	The posterior sample histogram of the $\mu$ of each segment divided by the change point and the displacement measured by the tape are shown in Fig. \ref{fig_v_bd9_3_up_mu} and Table \ref{tab_measured_height_9_3}, respectively.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_exp1_idx}
		\caption{Index values of different index-based detection methods in field experiment 1.}
		\label{fig_v_exp1_idx}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_mu}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 1.}
		\label{fig_v_bd9_3_up_mu}
	\end{figure} 
	\begin{table}[htbp]
		\centering
		%	\fontsize{6.5}{8}\selectfont
		\begin{threeparttable}
			\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 1, unit (mm).}
			\label{tab_measured_height_9_3}
			\begin{tabular}{ccccccccc}
				\toprule
				&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
				\midrule
				\multirow{3}*{Step 1} 
				& & ${h_0}$    &371.0&370.9&370.9&371.1&370.9&370.96\\
				& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
				& & $\Delta h$ & -30.0& -29.8& -29.4& -29.2& -29.9&-29.66\\
				\hline
				\multirow{3}*{Step 2} 
				& & ${h_0}$    &340.5&340.1&340.0&340.0&340.1&340.14\\
				& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
				& & $\Delta h$ &-27.5& -27.2& -27.1& -27.0& -27.1& -27.18\\
				\bottomrule
			\end{tabular}
		\end{threeparttable}
	\end{table}

@@

	As can be seen from Fig. \ref{fig_v_bd9_4_up_ts} and Table \ref{tab_measured_height_9_4}, the amplitude of the two displacements is smaller than that of the previous experiment. 
	The time series are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling. The results are shown in Fig. \ref{fig_v_bd9_4_up_tau}, \ref{fig_v_bd9_4_up_mu}, and \ref{fig_v_bd9_4_up_sigma}.

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_tau}
		\caption{Posterior sample distribution of $\tau$ in field experiment 2.}
		\label{fig_v_bd9_4_up_tau}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_mu}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 2.}
		\label{fig_v_bd9_4_up_mu}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_sigma}
		\caption{Histogram of posterior \textcolor{r_s}{samples} of $\sigma$ in field experiment 2.}
		\label{fig_v_bd9_4_up_sigma}
	\end{figure}
	Due to the decrease of displacement amplitude, the results are not as good as the previous experimental results. 
	It can be seen from Fig. \ref{fig_v_bd9_4_up_tau} that there are two peaks in the posterior sample distribution of $\tau_1$. Unlike Fig. \ref{fig_v_bd9_3_up_tau} of the previous experimental results, the two peaks are far away from each other, exceeding 500 s. 
	Accordingly, there are two peaks in the posterior sample distribution of $\mu_0$, $\mu_1$ and $\sigma$. 
	In addition, we found that the second peak of $\tau_1$ is very close to the peak of $\tau_2$, which is not what we want because we do not want to get very short segments. 
	In the next section, we will discuss adding a prior to the model to improve the performance of Bayesian inference.
	\section{Discussion}
	\label{disc}
	In field experiment 1, there are two significant peaks in the posterior sample distribution at the same change point. 
	In addition, in field experiment 2, the posterior distribution interval of two different change points is close.
	Here, the interval between adjacent change points is constrained by adding a prior. 
	A random variable $d\tau$, the distance between continuous change points, is added, which obeys the  discrete uniform distribution.

	\begin{equation}\label{eq_bayesian_prior_d_tau}
	P(d\tau_{i})=DiscreteU(\tau_{i} + d,\tau_{i+1})
	\end{equation}
	where $d$ is the shortest time interval to be constrained. The new Bayesian probability model with the prior is shown in Fig. \ref{fig_v_simple_p_model_add_new_rule}.

	\begin{figure}[H]
		\centering
		\includegraphics[scale=0.45]{v_simple_p_model_add_new_rule}
		\caption{ \textcolor{r_s}{Probability} model for displacement detection with an interval constraint prior.}
		\label{fig_v_simple_p_model_add_new_rule}
	\end{figure} 
	As shown in (\ref{eq_bayesian_prior_d_tau}) and Fig. \ref{fig_v_simple_p_model_add_new_rule}, the prior distribution of newly added random variables depends on the change points and the constraint interval. 
	In the following data processing, the interval $d$ is set to 300.
	The data in \textcolor{r_s}{the} field experiment 1 is reprocessed with the new Bayesian model, and the posterior distribution of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau_add_new_rule}.

@@

	As can be seen from the above discussion that the interval constraint prior can effectively improve the identifiability of change points.
	\textcolor{r_s}{
		This is the first time that Bayesian inference has been used for displacement detection based on GNSS kinematic positioning.
		Compared with indicator-based detection methods, this method has high robustness and flexibility.
		The method based on Bayesian inference uses multi-epoch observation data, which is more reliable.
		On the other hand, the Bayesian inference-based displacement detection method proposed in this paper is flexible enough to meet different analysis needs by adding a priori.
	}

	\section{Conclusions}
	\label{concl}
	This study set out to develop a Bayesian model for displacement detection from GNSS kinematic positioning. 
	The description of multiple displacements is given, and the Bayesian model for multiple displacement detection is proposed.
	The principle of Bayesian inference and its implementation based on MCMC sampling are presented.
	To provide epoch by epoch coordinate time series for displacement detection, the principle of GNSS kinematic positioning mode RTK is introduced.
	The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
	Simulation and field experiments were carried out to verify the effectiveness of the proposed method. 
	These experiments confirmed the effectiveness of the method in displacement identification and extraction.

	Significant displacements can be effectively detected by the displacement Bayesian inference model.
	The displacement is obtained by the difference of the mean of the coordinates before and after the change point, which can be obtained by the mean of the posterior sample.
	The accuracy of the final displacement is determined by the number of available samples before and after the change point.
	The more samples are, the higher the accuracy is.

	When the amplitude of displacement is small, the posterior distribution of change points appears multiple peaks, which is not conducive to the effective identification of change points.
	By adding an interval constraint prior, the influence of secondary change points can be effectively weakened.
	To reduce the influence of the sample points of the secondary change point on the displacement extraction, the coordinate mean before and after the change point can be estimated by the median of the posterior sample.

	The displacement detection based on Bayesian inference can meet different needs by adding a priori, and has sufficient flexibility.
	In addition, the Bayesian inference implementation based on MCMC sampling used in this paper provides posterior samples, which is more conducive to problem analysis.
	This study provides the first comprehensive assessment of the Bayesian inference model for displacement identification and extraction from GNSS kinematic positioning.
	\textcolor{r_s}{
	Although the method is verified with GNSS kinematic data, the method is also suitable for long-term displacement detection. The main difference is the error model and influencing factors considered, which will be carried out in the follow-up work.	
	}

>>>>

	\subsection{Simulation Experiment}
	In the experiment, we only simulate the up coordinate component, in which Gaussian white noise with the mean of 0 mm and the standard deviation of 30 mm is added.
	At 1000 s, 2500 s, and 3200 s, the displacements of -50 mm, -50 mm, and 100 mm are added, respectively. 
	The simulation results are shown in Fig. \ref{fig_v_sim_simple_gauss_ts}.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_sim_simple_gauss_ts}
		\caption{Simulation data with multiple displacement change points.}
		\label{fig_v_sim_simple_gauss_ts}
	\end{figure} 
	As shown in Fig. \ref{fig_v_sim_simple_gauss_ts}, the whole time series is divided into four segments by three displacement change points. 
	\textcolor{r_s}{The time series is processed by the proposed method, and Bayesian inference is realized through MCMC sampling using the probability model designed above.} 
	The posterior sample distribution of $\bf{\tau}$ is shown in Fig. \ref{fig_v_tau_sim_simple}.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_tau_sim_simple}
		\caption{Posterior sample distribution of $\tau$ in the simulation experiment.}
		\label{fig_v_tau_sim_simple}
	\end{figure}

	As can be seen from Fig. \ref{fig_v_tau_sim_simple}, \textcolor{r_s}{there are more samples at the displacement, and} all the designed displacement change points are identified. 
	$\tau_3$ is the easiest to \textcolor{r_s}{identify}, mainly due to \textcolor{r_s}{its maximum} displacement amplitude. 
	  \textcolor{r_s}{Due to the smaller displacement amplitude and fewer samples on the right at $\tau_2$}, the estimated accuracy is worse than the other two change points.
	The histogram of the posterior sample of $\bf{\mu}$ is shown in Fig. \ref{fig_v_mu_sim_simple}.

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_mu_sim_simple}
		\caption{Histogram of posterior estimation of $\mu$ in the simulation experiment.}
		\label{fig_v_mu_sim_simple}
	\end{figure} 
	The blue curve in Fig. \ref{fig_v_mu_sim_simple} is the fitting result of \textcolor{r_s}{the} Gaussian distribution of the histogram.
	Although we assume that the prior distribution of $\bf{\mu}$ in the model obeys a uniform distribution, the posterior sample approximately obeys normal distribution. 
	The vertical green dashed line in Fig. \ref{fig_v_mu_sim_simple} represents the mean value of posterior samples, and the mean values of the four segments are 1.17 mm, -49.58 mm, -98.9 mm, and -3.65 mm.
	Among these means, $\mu_2$ has the highest accuracy, and its corresponding posterior sample coverage is the narrowest. 
	The estimation accuracy of $\mu_4$ is the lowest, and the corresponding posterior sample coverage is the widest. 
	These are mainly due to the fact that most samples are used for $\mu_2$ estimation, while least samples are used for $\mu_4$ estimation. 
	As shown in Fig. \ref{fig_v_sigma_sim_simple}, $\sigma$ is also accurately estimated.

	% 仿真实验中不同基于索引检测方法的指标值如图6所示。
	% 从中可以看出不同探测方法所采用的指标的数值范围不一致，但在所设计的突变处很明显。
	%  然而，想基于这些指标值自动将这些突变点识别出来，还需要额外的工作。
	%  另外，这些方法设计之初为了探测突变点，并未涉及位移提取。
	%  有学者，基于设计了基于这些指标的突变探测和位移提取方法，但实时过程复杂。
	%  相比而言，本文提出的方法是一种简单直接易于实现的一站式方法。
	The index values of different index-based detection methods in the simulation experiment are shown in Fig. \ref{fig_v_sim_idx}.
	It can be seen that the numerical range of indicators used by different \textcolor{r_s}{index-based} detection methods is not consistent, but all are obvious at the designed abrupt point.
	However, to automatically identify these abrupt points based on these index values, additional work is required, such as setting a certain threshold  \textcolor{r_s}{or detection window\cite{shen_shortterm2021}}.
	In addition, these methods were originally designed to detect abrupt points without involving displacement extraction.
	There are abrupt detection and displacement extraction methods based on these indicators, but the implementation process is complex\cite{shen_shortterm2021}.
	In contrast, the method proposed in this work is a simple, straightforward, and easy-to-implement one-stop method.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_sigma_sim_simple}
		\caption{Histogram of posterior sample of $\sigma$ in the simulation experiment.}
		\label{fig_v_sigma_sim_simple}
	\end{figure} 
	\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.45]{v_sim_idx}
	\caption{Index values of different index-based detection methods in simulation experiments.}
	\label{fig_v_sim_idx}
	\end{figure} 
	\subsection{Field Experiments}
	The experiments were carried out on the roof of a building on the campus of Wuhan University, and the equipment deployment is shown in Fig. \ref{fig_v_field_exp_config}. 
	A hard plank was pressed with large stones to ensure that the plank remains as fixed as possible during moving the object hanging on the plank. 
	One receiver antenna was fixed on the plank as a rover, and the other receiver antenna was installed on a tripod beside it as the base station. 
	Both antennas were connected to BD992 OEM boards on the table, and the OEM boards were connected to the laptops for data collection. 
	As shown in subgraphs (c) and (d), the height of the antenna was measured with a tape before and after each movement of the object hanging on the plank. 
	\textcolor{r_s}{
		The minimum scale of the tape is 1 mm, that is, the accuracy of the tape is 1 mm, and the estimated reading is 0.1 mm.
		Take five readings for each measurement to ensure the accuracy and reliability of the data.
	}
	Besides, markers are made on the ground and on the antenna respectively to ensure that the same position was referenced for each measurement. 
	The sampling frequency of the GNSS receiver is set to 1 Hz. 
	We did two experiments, each lasting nearly 45 minutes. 
	During the experiment, the object hanging on the board was manually moved several times.
	The displacement amplitude of the second experiment is smaller than that of the first experiment.
	The GNSS observation data collected above are processed by the open-source software RTKLIB\cite{takasu2011rtklib}. 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.5]{v_field_exp_config}
		\caption{Filed experiment configuration. (a) Overview; (b) Working platform; (c) Displacement control platform; (d) Displacement measurement by tape. }
		\label{fig_v_field_exp_config}
	\end{figure}

	\subsubsection{Field Experiment 1}%rover_bd9_3
	GNSS observations were processed epoch by epoch by using RTK mode, and the results are shown in Fig. \ref{fig_v_bd9_3_up_tau}.
	Only the vertical displacement was triggered in the experiment, so only the up coordinate component is displayed. 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_ts}
		\caption{The up component of coordinates obtained by RTK positioning in field experiment 1.}
		\label{fig_v_bd9_3_up_ts}
	\end{figure}

	For such a short baseline, most of the errors can be eliminated by the double-difference observation. 
	As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as the multipath error that have not been eliminated. 
	\textcolor{r_s}{The RTK positioning results are served as the input of displacement detection}, and Bayesian inference is implemented by the MCMC sampling. 
	The histogram of the posterior sample of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau}.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_tau}
		\caption{Posterior sample distribution of $\tau$ in field experiment 1.}
		\label{fig_v_bd9_3_up_tau}
	\end{figure} 
	From the posterior sample distribution of $\tau_2$ in Fig. \ref{fig_v_bd9_3_up_tau}, one of the change points can be identified as 1897 s. 
	According to the maximum value in the bar chart of the posterior sample of $\tau_1$, the change point is identified as 781 s.
	However, as can be seen from Fig. \ref{fig_v_bd9_3_up_tau}, there are two peaks in the posterior sample distribution of change point $\tau_1$.
	The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object. 
	In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}. 
	The index values of different index-based detection methods in \textcolor{r_s}{the} field experiment 1 are shown in Fig. \ref{fig_v_exp1_idx}. At the abrupt point, each index value is no longer as clear as in the simulation experiment, which puts forward higher requirements for additional analysis of these indexes.
	The posterior sample histogram of the $\mu$ of each segment divided by the change point and the displacement measured by the tape are shown in Fig. \ref{fig_v_bd9_3_up_mu} and Table \ref{tab_measured_height_9_3}, respectively.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_exp1_idx}
		\caption{Index values of different index-based detection methods in field experiment 1.}
		\label{fig_v_exp1_idx}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_mu}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 1.}
		\label{fig_v_bd9_3_up_mu}
	\end{figure} 
	\begin{table}[htbp]
		\centering
		%	\fontsize{6.5}{8}\selectfont
		\begin{threeparttable}
			\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 1, unit (mm).}
			\label{tab_measured_height_9_3}
			\begin{tabular}{ccccccccc}
				\toprule
				&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
				\midrule
				\multirow{3}*{Step 1} 
				& & ${h_0}$    &371.0&370.9&370.9&371.1&370.9&370.96\\
				& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
				& & $\Delta h$ & -30.0& -29.8& -29.4& -29.2& -29.9&-29.66\\
				\hline
				\multirow{3}*{Step 2} 
				& & ${h_0}$    &340.5&340.1&340.0&340.0&340.1&340.14\\
				& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
				& & $\Delta h$ &-27.5& -27.2& -27.1& -27.0& -27.1& -27.18\\
				\bottomrule
			\end{tabular}
		\end{threeparttable}
	\end{table}

@@

	As can be seen from Fig. \ref{fig_v_bd9_4_up_ts} and Table \ref{tab_measured_height_9_4}, the amplitude of the two displacements is smaller than that of the previous experiment. 
	\textcolor{r_s}{The RTK positioning results are served as the input of displacement detection}, and Bayesian inference is implemented by the MCMC sampling. The results are shown in Fig. \ref{fig_v_bd9_4_up_tau}, \ref{fig_v_bd9_4_up_mu}, and \ref{fig_v_bd9_4_up_sigma}.

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_tau}
		\caption{Posterior sample distribution of $\tau$ in field experiment 2.}
		\label{fig_v_bd9_4_up_tau}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_mu}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 2.}
		\label{fig_v_bd9_4_up_mu}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_sigma}
		\caption{Histogram of posterior \textcolor{r_s}{samples} of $\sigma$ in field experiment 2.}
		\label{fig_v_bd9_4_up_sigma}
	\end{figure}
	Due to the decrease of displacement amplitude, the results are not as good as the previous experimental results. 
	It can be seen from Fig. \ref{fig_v_bd9_4_up_tau} that there are two peaks in the posterior sample distribution of $\tau_1$. Unlike Fig. \ref{fig_v_bd9_3_up_tau} of the previous experimental results, the two peaks are far away from each other, exceeding 500 s. 
	Accordingly, there are two peaks in the posterior sample distribution of $\mu_0$, $\mu_1$ and $\sigma$. 
	In addition, we found that the second peak of $\tau_1$ is very close to the peak of $\tau_2$, which is not what we want because we do not want to get very short segments. 
	In the next section, we will discuss adding a prior to the model to improve the performance of Bayesian inference.
	In the next section, we will discuss adding a prior to the \textcolor{r_s}{probability} model to improve the performance of the \textcolor{r_s}{displacement detection method}.
	\section{Discussion}
	\label{disc}
	In field experiment 1, there are two significant peaks in the posterior sample distribution at the same change point. 
	In addition, in field experiment 2, the posterior distribution interval of two different change points is close.
	Here, the interval between adjacent change points is constrained by adding a prior. 
	A random variable $d\tau$, the distance between continuous change points, is added, which obeys the  discrete uniform distribution.

	\begin{equation}\label{eq_bayesian_prior_d_tau}
	P(d\tau_{i})=DiscreteU(\tau_{i} + d,\tau_{i+1})
	\end{equation}
	where $d$ is the shortest time interval to be constrained. The new \textcolor{r_s}{probability} model with the prior is shown in Fig. \ref{fig_v_simple_p_model_add_new_rule}.

	\begin{figure}[H]
		\centering
		\includegraphics[scale=0.45]{v_simple_p_model_add_new_rule}
		\caption{ \textcolor{r_s}{Probability} model for displacement detection with an interval constraint prior.}
		\label{fig_v_simple_p_model_add_new_rule}
	\end{figure} 
	As shown in (\ref{eq_bayesian_prior_d_tau}) and Fig. \ref{fig_v_simple_p_model_add_new_rule}, the prior distribution of newly added random variables depends on the change points and the constraint interval. 
	In the following data processing, the interval $d$ is set to 300.
	The data in \textcolor{r_s}{the} field experiment 1 is reprocessed with the new \textcolor{r_s}{probability} model, and the posterior distribution of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau_add_new_rule}.

@@

	As can be seen from the above discussion that the interval constraint prior can effectively improve the identifiability of change points.
	\textcolor{r_s}{
		This is the first time that Bayesian inference has been used for displacement detection based on GNSS kinematic positioning.
		Compared with indicator-based detection methods, this method has high robustness and flexibility.
		The method based on Bayesian inference uses multi-epoch observation data, which is more reliable.
		On the other hand, the Bayesian inference-based displacement detection method proposed in this paper is flexible enough to meet different analysis needs by adding a priori. Although only the vertical direction has been verified due to the experimental equipment, the horizontal direction should also be adapted because the vertical direction is noisier.
	}

	\section{Conclusions}
	\label{concl}
	This study set out to develop a \textcolor{r_s}{displacement detection approach} from GNSS kinematic positioning. 
	\textcolor{r_s}{GNSS kinematic positioning is used to provide epoch by epoch coordinate time series for displacement detection.}
	The principle of Bayesian inference and its implementation based on MCMC sampling are presented.
	The description of multiple displacements is given, and the \textcolor{r_s}{probability} model for multiple displacement detection is proposed.
	The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
	Simulation and field experiments were carried out to verify the effectiveness of the proposed method. 
	These experiments confirmed the effectiveness of the method in displacement identification and extraction.

	Significant displacements can be effectively detected by the displacement \textcolor{r_s}{detection method}.
	The displacement is obtained by the difference of the mean of the coordinates before and after the change point, which can be obtained by the mean of \textcolor{r_s}{posterior samples}.
	The accuracy of the final displacement is determined by the number of available samples before and after the change point.
	The more samples are, the higher the accuracy is.

	When the amplitude of displacement is small, the posterior distribution of change points appears multiple peaks, which is not conducive to the effective identification of change points.
	By adding an interval constraint prior, the influence of secondary change points can be effectively weakened.
	To reduce the influence of \textcolor{r_s}{samples} of the secondary change point on the displacement extraction, the coordinate mean before and after the change point can be estimated by the median of \textcolor{r_s}{posterior samples}.

	The displacement detection \textcolor{r_s}{method} based on Bayesian inference can meet different needs by adding a priori, and has sufficient flexibility.
	In addition, the Bayesian inference implementation based on MCMC sampling used in this paper provides posterior samples, which is more conducive to problem analysis.
	This study provides the first comprehensive assessment of the Bayesian inference \textcolor{r_s}{based method} for displacement identification and extraction from GNSS kinematic positioning.
	\textcolor{r_s}{
	Although the method is verified with GNSS kinematic data, the method is also suitable for long-term displacement detection. The main difference is the probability model and influencing factors considered, which will be carried out in the follow-up work.	
	}
